### 2017-07-21 Dokumentation/1_Paper/Paper.tex
Quellenangabe ergänzt
Korrektur
Kleine Korrektur bei Texturen Links

\subsection{Zusammenfassung}

@@

\begin{appendix}
\section{Anhang}
\todo{Autor: Svenja}
	Anhang mit Lizenzen usw.

@@

air_conditioning:
https://www.textures.com/download/aircos0097/63182?q=air+con
(last viewed: 2017-07-14)

asphalt_damaged:
https://www.textures.com/download/asphaltdamaged0059/46538?q=asphalt+damaged
(last viewed: 2017-07-14)

back_door:
https://www.textures.com/download/doorswood0128/64000?q=DoorsWood0128
(last viewed: 2017-07-14)

brown_concrete:
https://www.textures.com/download/substance0066/128441?q=concrete+brown
(last viewed: 2017-07-14)

concrete_bare2:
https://www.textures.com/download/concretebare0280/35243?q=ConcreteBare0280
(last viewed: 2017-07-14)

front_door:
https://www.textures.com/download/doorswood0125/50420?q=door
(last viewed: 2017-07-14)

@@

metal_plates:
https://www.textures.com/download/metalplatesbare0154/123165?q=MetalPlatesBare0154
(last viewed: 2017-07-14)

plywood_painted-green:
https://www.textures.com/download/plywoodpainted0024/5719?q=plywood+painted
(last viewed: 2017-07-14)

plywood_painted-white:
https://www.textures.com/download/plywoodpainted0057/59134?q=plywood+painted+white
(last viewed: 2017-07-14)

rough_bricks:
https://www.textures.com/download/3dscans0037/126993?q=rough+bricks
(last viewed: 2017-07-14)

@@

>>>>

@@

\begin{appendix}
\section{Anhang}

@@

air\_conditioning:
https://www.textures.com/download/aircos0097/63182?q=air+con
(last viewed: 2017-07-14)

asphalt\_damaged:
https://www.textures.com/download/asphaltdamaged0059/46538?q=asphalt+damaged
(last viewed: 2017-07-14)

back\_door:
https://www.textures.com/download/doorswood0128/64000?q=DoorsWood0128
(last viewed: 2017-07-14)

brown\_concrete:
https://www.textures.com/download/substance0066/128441?q=concrete+brown
(last viewed: 2017-07-14)

concrete\_bare2:
https://www.textures.com/download/concretebare0280/35243?q=ConcreteBare0280
(last viewed: 2017-07-14)

front\_door:
https://www.textures.com/download/doorswood0125/50420?q=door
(last viewed: 2017-07-14)

@@

metal\_plates:
https://www.textures.com/download/metalplatesbare0154/123165?q=MetalPlatesBare0154
(last viewed: 2017-07-14)

plywood\_painted-green:
https://www.textures.com/download/plywoodpainted0024/5719?q=plywood+painted
(last viewed: 2017-07-14)

plywood\_painted-white:
https://www.textures.com/download/plywoodpainted0057/59134?q=plywood+painted+white
(last viewed: 2017-07-14)

rough\_bricks:
https://www.textures.com/download/3dscans0037/126993?q=rough+bricks
(last viewed: 2017-07-14)

@@

\subsubsection{Straßenverkehr}

strassenoberfläche:
http://www.bildburg.de/texturen/boden/strassen/
(last viewed: 2017-07-20)
